\numberlist{

	\item \question{What is Python? What are the benefits of using Python?}
	\answer{Python is a high-level, interpreted, general-purpose programming language. Being a
general-purpose language, it can be used to build almost any type of application with
the right tools/libraries. Additionally, python supports objects, modules, threads,
exception-handling, and automatic memory management which help in modelling
real-world problems and building applications to solve these problems.

	\textbf{Benefits of using Python:}
	\newlist{
	\item Python is a general-purpose programming language that has a simple, easy-to-learn syntax that emphasizes readability and therefore reduces the cost of program maintenance. Moreover, the language is capable of scripting, is completely open-source, and supports third-party packages encouraging modularity and code reuse.	

	\item Its high-level data structures, combined with dynamic typing and dynamic binding, attract a huge community of developers for Rapid Application Development and deployment.		
	}	
	
	}
	
	
	\item \question{What is a dynamically typed language?}
	
	\answer{
	Before we understand a dynamically typed language, we should learn about what typing is. Typing refers to type-checking in programming languages. In a strongly-typed language, such as Python, "1" + 2 will result in a type error since these
languages don't allow for "type-coercion" (implicit conversion of data types). On the other hand, a weakly-typed language, such as Javascript, will simply output "12" as result.


	\textbf{Type-checking can be done at two stages} -
	
	\newlist{
		\item Static - Data Types are checked before execution.
		\item Dynamic - Data Types are checked during execution.

	}

	Python is an interpreted language, executes each statement line by line and thus type-checking is done on the fly, during execution. Hence, Python is a Dynamically Typed Language.

	}	
	
	

}